### 2012-12-20 doc/description.tex
structural changes in document

 \inference{ cardinality(p) > 1 \wedge ! mandatory(p) \\ \wedge \exists t : t = table(name(owningClass(p)), d)}{\begin{gathered}tables(d) \cup  table(name(p), primaryKey("Id"), column("value", \rho_t(type(p))), \\ foreignKey(name(p), name(owningClass(p)), \varnothing) \\

@@

This section defines eORM for each trivial operation evolving application from \ref{sec:appEvolution}, moreover there are described more complex cases of evolution.

\subsection{Evolution of Application}
\label{sec:appEvolution}

>>>>

 \inference{ cardinality(p) > 1 \wedge ! mandatory(p) \\ \wedge \exists t : t = table(name(owningClass(p)), d)}{\begin{gathered}tables(d) \cup  table(name(p), primaryKey("Id"), column("value", \rho_t(type(p)), \varnothing), \\ foreignKey(name(p), name(owningClass(p)), NOTNULL) \\

@@

\section{Evolution}
\subsection{Evolution of Application}
\label{sec:appEvolution}
